Prediction of Early Periprosthetic Joint Infection after Total Hip Arthroplasty: a simplified and externally validated model based on observational registry data from Sweden and Denmark

### 2021-05-26 reports/article.Rmd
version to share

**PARTICIPANTS AND METHODS:** This prediction model was derived on `r nmbr(N_shar)` patients from the Swedish Hip Arthroplasty Register and validated on `r nmbr(N_dk)` patients from the Danish Hip Arthroplasty Register. Data on comorbidities and socioeconomic background variables on all patients were obtained from the National Registers and. Logistic least absolute shrinkage and selection operator (LASSO) regression was applied to develop prediction models for PJI within 90 days after surgery. We assessed model performance by the area under the receiver operation characteristics curve (AUC), calibration belt plots and the fraction of new information.

**RESULTS:** The crude incidence rate of PJI after THA was `r crude_rate * 100` % within 90 days in the Swedish derivation cohort. A prediction model for PJI within 90 days combined `r coefs_text`, resulting in an `r get_auc("Reduced model", "2")` internally and `r sub("^AUC = ", "", get_auc("Reduced model", "2", Country = "Denmark"))` externally. These models were superior to traditional models based on the American Society for Anesthesiologists (ASA) classification `r get_auc("ASA")`, or the Charlson `r get_auc("Charlson")`, Elixhauser `r get_auc("Elixhauser")`, and Rx Risk V `r get_auc("Rx Risk")` comorbidity indices.

@@

Periprosthetic joint infection (PJI) is the most devastating of early complications after total hip arthroplasty (THA), mainly due to its severity in terms of increased mortality, the required number of re-operations, long-term antibiotic treatment, and often persistently impaired quality of life.[@Zimmerli2006; @Kapadia2016; @Shohat2019] Many risk factors for the development of PJI are identified, with anaemia, diabetes, and obesity being important, to some extent modifiable risk factors, whereas advanced age and male gender are examples of non-modifiable risk factors.[@Ridgeway2005; @Lai2007; @Malinzak2009; @Ong2009; @Pedersen2010; @Bozic2012; @Jamsen2012; @Rasouli2014a; @Maoz2015] Individualized PJI risk stratification would be a highly desirable tool in the pre-operative assessment of patients scheduled for THA, but established measures of comorbidity such as the American Society for Anesthesiologists' (ASA) classification or considerably more complex comorbidity indices cannot be used in this context. Although high ASA class is a risk factor associated with development of PJI, this classification is imprecise, and it was never developed for the purpose of predicting this specific complication.[@Haynes1995; @Berbari2012] The Charlson[@Charlson1987] and Elixhauser[@Elixhauser1998] comorbidity indices are based on `r nrow(coder::charlson)` or `r nrow(coder::elixhauser)` conditions according to the International Classification of Diseases (ICD), respectively, but they are cumbersome to use in a clinical setting, and they were also not designed for prediction of specific adverse events after THA. The same is true for the Rx Risk V-classification with `r nrow(coder::rxriskv)` conditions codified along the Anatomical Therapeutic Chemical (ATC) Classification.[@Sloan2003; @Pratt2018] Several attempts have been made at developing individualized risk prediction models for clinical usage, with the Universal American College of Surgeons National Surgical Quality Improvement Program (ACS NSQIP) Surgical Risk Calculator being one of the first.[@Edelstein2015; @Wingert2016a] Several other risk calculators for the risk of PJI after THA have since been derived on US or Australian cohorts, but none has gained general acceptance.[@Wingert2016a; @Bozic2013a; @Inacio2015a] This is mainly due to often limited, sometimes single-center based samples, low discriminative ability or low accuracy of the prediction models, or the absence of external model validation. Thus, there is an urgent need for improved prediction models of PJI. We therefore developed a prediction model of PJI within 90 days after THA that is based upon easily accessible data that are available in the setting of clinical decision-making.

@@

We used data from the Swedish Hip Arthroplasty Register (SHAR) for model derivation and internal validation of discrimination and calibration. The best models were then validated externally on a cohort from the Danish Hip Arthroplasty Register (DHR).

@@

The derivation cohort was obtained from patients recorded in the SHAR `r period` with the choice of 2008 as the starting year because registration of ASA class and body mass index (BMI) in the SHAR was initiated then. Deterministic data linkage was achieved by using personal identity numbers that are assigned to all Swedish residents at birth or immigration.[@Ludvigsson2009; @Cnudde2016] The diagnosis underlying the index THA procedure (categorized into `r glue::glue_collapse(tolower(levels(df$P_DiaGrp)), ", ", last = " and ") %>% {gsub("\\(avn\\)", "[AVN]", .)}`), type of THA fixation (cemented or uncemented stem and cup respectively), age at index surgery, sex, BMI, ASA class, type of hospital, and year of surgery, were obtained from the SHAR. Data on comorbidities for one year prior to index surgery were obtained from the National Patient Register (NPR) where diagnoses based on in- and outpatient episodes in all private and public hospitals are coded according to the ICD-10 together with admission and discharge dates. Data on marital status and the educational level of patients was obtained from the longitudinal integration database for health insurance and labour market studies (LISA) from Statistics Sweden. The SHAR has completeness of 96-98 % and 100 % coverage,[@Karrholm2018] the LISA has coverage of 98 % with 85 % accuracy, and completeness for the NPR is above 99 % and the positive predictive value is 85-95 %.[@Ludvigsson2011] Death dates were linked from the national population register. Only the last operated hip was considered for patients with bilateral THA.[@Bulow2020] Patients with missing information on, or an ASA class of IV and above, were excluded, as were patients with missing information on BMI or a measurement above 50. Patients with missing information on educational levels or the type of hospital performing index surgery were also excluded.

@@

Logistic LASSO regression was performed for each sample using the chosen $\lambda$ as penalty term. Regression coefficients were ranked based on their absolute values as a measure of variable importance. We then used Bayesian methods to estimate a posterior distribution and to identify two change points in a linear segmented piecewise regression model. The second change point was then used as a break-point. Influential predictors with absolute coefficients value above this point scored a point and the entire process was repeated 100 times, yielding 10,000 bootstrap samples in total. Potential predictors that were selected at least `r brlasso_selection_n["main"]` out of 100 times were then used in a main effects multivariable logistic regression model without penalty and without pre-normalization of numeric variables. An even more parsimonious "reduced" model with potential predictors chosen at least `r brlasso_selection_n["reduced"]` out of 100 times was evaluated for comparison. Univariable prediction models based on either ASA class, the Charlson, Elixhauser, or the Rx Risk V comorbidity indices were fitted for comparison, as well as multivariable models combining those measures with age, gender and BMI (10 models in total). The Rx Risk V index is a comorbidity index based on medical prescriptions coded by the Anatomical Therapeutic Chemical (ATC) classification system during one year prior to surgery. This data was retrieved from the Swedish national prescription register and classified according to Pratt et al.[@Pratt2018] Odds ratios for the final models were estimated with 95 % confidence intervals.

@@

**TODO:: Add XXX numbers frmo DK. Differences in Charlson/Elix might be discussed?**

@@

We found that a reduced prediction model based on some easily identifiable clinical conditions, gender, and BMI was better at predicting PJI within 90 days after THA than models based on either ASA class or the Charlson, Elixhauser or Rx Risk V comorbidity indices. This model performed better than the established comorbidity measures in terms of AUC, Nagelkerke's $R^2$ and calibration.

@@

Since the prediction model was based on easily accessible information it can be translated into a simple formula $\hat p = 1/(1 + e^{-\hat \alpha - \mathbf{\hat \beta X}})$ where $\hat p$ is the estimated probability, $\hat \alpha$ and $\mathbf{\beta} = \hat\beta_1, \hat\beta_2, \ldots, \hat\beta_k$ are the estimated intercept and coefficients (Tab. \@ref(tab:coefs)) and $\mathbf{X} = X_1, X_2, \ldots, X_k$ are corresponding patient characteristics. For example, `r examples$desc[[1]]` would have a probability of `r examples$p[[1]]` of suffering from a PJI within 90 days, whereas `r examples$desc[[2]]` would have a probability of `r examples$p[[2]]`. Note, however, that observed proportions above 10 % were rare, and predicted probabilities above this limit are subject to extrapolation.

@@

Male gender is associated with an increased risk of developing PJI after arthroplasty surgery,[@Dale2012] and gender is included as a predictor variable in several previously developed risk calculators, which agrees with our findings.[@Wingert2016a; @Tan2018] Patients with liver cirrhosis are described to have a more than doubled risk of suffering from PJI within one year after THA, supporting our finding of the presence of liver diseases among our predictor variables.[@Deleuran2015] Taken together, the above cited findings support that the predictor variables in our models seem to be relevant in the context of predicting PJI.

@@

```{r aucci, fig.cap = "Area Under the Receiver Operation Characteristics Curve (AUC) as a measure of predictive discriminative ability with 95 % confidence intervals (De-Long). The reduced model performed no different than the main model on the Swedish data, and both of these models performed better than all other models (left panel). Similar models were fitted to the Danish cohort (right panel). Coefficient values based on the Swedish data, Reduced model (SE), performed almost as good as Reduced model (DK) with coefficient values refitted to the Danish cohort."}

@@

```{r sep, fig.cap = "The vast majority of patients did not have PJI. Hence, the blue bars dominate the histograms (left panel; note the scales). A normalized density plot reveals however, that patients with PJI had, on average, higher estimated probabilities for this adverse event (lower panels)."}
knitr::include_graphics("../graphs/separation.png")
```

@@

```{r calibrationse, fig.cap = "This figure illustrates internal calibration of the reduced model, used in the Swedish cohort. Predicted probabilities are similar to observed proportions."}
knitr::include_graphics("../graphs/calibration.png")
```

@@

tibble(
  classification = c("ICD-10", "NOMESCO"),
  codes = c(icd10_codes, nomesco_codes)
) %>% 
  knitr::kable(
    caption = "Codes identifying infection if recorded in the national patient register within 90 days or 2 years after THA respectively."
  )

@@

```{r fni}
tab_new_info %>% 
  arrange(desc(`R2 (%)`)) %>% 
knitr::kable(
  caption = "Nagelkerke's pseudo-coefficient of determination (R2) as an estimate of the proportion of explained variance for each model (the correlation between observed and predicted values). The univariable Charlson model had the lowest R2 and was therefore used as reference for the fraction of new information (FNI) added by the other models.")
```

@@

```{r coefs}
tbl_coefs_present %>% 
  mutate(
    beta = round(beta, 2)
  ) %>% 
knitr::kable(
  caption = 'Estimated coefficients (beta) and odds ratios (OR) with 95 % confidence intervals for the reduced models. BMI = body mass index (under/normal weight as baseline). CNS = central nervous system. Primary osteoarthritis was baseline for diagnosis and female was baseline for sex.'
)
```

@@

Variable selection and coefficient estimates were based on the Swedish cohort. 
The reduced model was then used to predict PJI also in Denmark. The coefficient values of the reduced model were also re-fitted to the Danish cohort for comparison. We compared the estimates from the Swedish and Danish cohort and found most values to be of similar magnitude. The only coefficient with reversed direction was for patients with a diagnose of "sequelae after childhood hip disease". This is a rare condition, with very few observed PJI:s within 90 days. We also re-estimated the model coefficients 1,000 times based on the Swedish data. Each time, we took a random sample of the same size, $N = 18854$, as was observed in the Danish cohort. The 2.5th and 97.5th percentiles were then used to form empirical 95 % confidence intervals for each coefficient ((Tab. \@ref(tab:comparecoefs)) and Fig. \@ref(fig:coefsspread)). It is seen that the estimated effect of the diagnose of "sequelae after childhood hip disease" fall outside this empirical CI. Applying multiplicity correction by Bonferroni or similar, would eliminate this significance. Hence, it seems that both cohorts are similar in respect to association between the studied covariates and the risk of PJI within 90 days of THA.

```{r comparecoefs}
compare_se_dk_coefs %>% 
knitr::kable(
  caption = ""
)
```

```{r coefsspread, fig.cap = "Estimated coefficient values for the reduced model. Red triangles indicate estimates from the Swedish derivation data set. Red circles indicate re-estimated coefficient values for the same model based on the Danish validation cohort. Small coulored dots are empirical estimates from 1000 subsamples based on the Swedish data set, of the same sample size as used in the Danish validation cohort. Black dots indicate the outer limits of empirical confidence intervals based on the 2.5th and 97.5th percentiles. It is seen that the Swedish and Danish estimates are similar. The Danish estimates almost always fall within the 95 % empirical CIs. The sole exception is for the rare diagnose group of 'sequelae after childhood hip disease'."}
knitr::include_graphics("../validation/Swedish_model.png")
```

>>>>

**PARTICIPANTS AND METHODS:** This prediction model was derived on `r nmbr(N_shar)` patients from the Swedish Hip Arthroplasty Register and validated on `r nmbr(N_dk)` patients from the Danish Hip Arthroplasty Register. Data on comorbidities and socioeconomic background variables on all patients were obtained from the National Registers. Logistic least absolute shrinkage and selection operator (LASSO) regression was applied to develop prediction models for PJI within 90 days after surgery. We assessed model performance by the area under the receiver operation characteristics curve (AUC), calibration belt plots and the fraction of new information.

**RESULTS:** The crude incidence rate of PJI after THA was `r crude_rate * 100` % within 90 days in the Swedish derivation cohort and **X.XX %** in Denmark. A prediction model for PJI within 90 days combined `r coefs_text`, resulting in an `r get_auc("Reduced model", "2")` internally and `r sub("^AUC = ", "", get_auc("Reduced model", "2", Country = "Denmark"))` externally. These models were superior to traditional models based on the American Society for Anesthesiologists (ASA) classification `r get_auc("ASA")`, or the Charlson `r get_auc("Charlson")`, Elixhauser `r get_auc("Elixhauser")`, and Rx Risk V `r get_auc("Rx Risk")` comorbidity indices.

@@

Periprosthetic joint infection (PJI) is the most devastating of early complications after total hip arthroplasty (THA), mainly due to its severity in terms of increased mortality, the required number of re-operations, long-term antibiotic treatment, and often persistently impaired quality of life.[@Zimmerli2006; @Kapadia2016; @Shohat2019] Many risk factors for the development of PJI are identified, with anaemia, diabetes, and obesity being important, to some extent modifiable risk factors, whereas advanced age and male sex are examples of non-modifiable risk factors.[@Ridgeway2005; @Lai2007; @Malinzak2009; @Ong2009; @Pedersen2010; @Bozic2012; @Jamsen2012; @Rasouli2014a; @Maoz2015] Individualized PJI risk stratification would be a highly desirable tool in the pre-operative assessment of patients scheduled for THA, but established measures of comorbidity such as the American Society for Anesthesiologists' (ASA) classification or considerably more complex comorbidity indices cannot be used in this context. Although high ASA class is a risk factor associated with development of PJI, this classification is imprecise, and it was never developed for the purpose of predicting this specific complication.[@Haynes1995; @Berbari2012] The Charlson[@Charlson1987] and Elixhauser[@Elixhauser1998] comorbidity indices are based on `r nrow(coder::charlson)` or `r nrow(coder::elixhauser)` conditions according to the International Classification of Diseases (ICD), respectively, but they are cumbersome to use in a clinical setting, and they were also not designed for prediction of specific adverse events after THA. The same is true for the Rx Risk V-classification with `r nrow(coder::rxriskv)` conditions codified along the Anatomical Therapeutic Chemical (ATC) Classification.[@Sloan2003; @Pratt2018] Several attempts have been made at developing individualized risk prediction models for clinical usage, with the Universal American College of Surgeons National Surgical Quality Improvement Program (ACS NSQIP) Surgical Risk Calculator being one of the first.[@Edelstein2015; @Wingert2016a] Several other risk calculators for the risk of PJI after THA have since been derived on US or Australian cohorts, but none has gained general acceptance.[@Wingert2016a; @Bozic2013a; @Inacio2015a] This is mainly due to often limited, sometimes single-center based samples, low discriminative ability or low accuracy of the prediction models, or the absence of external model validation. Thus, there is an urgent need for improved prediction models of PJI. We therefore developed a prediction model of PJI within 90 days after THA that is based upon easily accessible data that are available in the setting of clinical decision-making.

@@

We used data from the Swedish Hip Arthroplasty Register (SHAR) for model derivation and internal validation of discrimination and calibration. The best model was then validated externally on a cohort from the Danish Hip Arthroplasty Register (DHR).

@@

The derivation cohort was obtained from patients recorded in the SHAR `r period` with the choice of 2008 as the starting year because registration of ASA class and body mass index (BMI) was initiated then. Deterministic data linkage was achieved by using personal identity numbers that are assigned to all Swedish residents at birth or immigration.[@Ludvigsson2009; @Cnudde2016] The diagnosis underlying the index THA procedure (categorized into `r glue::glue_collapse(tolower(levels(df$P_DiaGrp)), ", ", last = " and ") %>% {gsub("\\(avn\\)", "[AVN]", .)}`), type of THA fixation (cemented or uncemented stem and cup respectively), age at index surgery, sex, BMI, ASA class, type of hospital, and year of surgery, were obtained from the SHAR. Data on comorbidities for one year prior to index surgery were obtained from the National Patient Register (NPR) where diagnoses based on in- and outpatient episodes in all private and public hospitals are coded according to ICD-10 together with admission and discharge dates. Data on marital status and the educational level of patients was obtained from the longitudinal integration database for health insurance and labour market studies (LISA) from Statistics Sweden. The SHAR has completeness of 96-98 % and 100 % coverage,[@Karrholm2018] the LISA has coverage of 98 % with 85 % accuracy, and completeness for the NPR is above 99 % and the positive predictive value is 85-95 %.[@Ludvigsson2011] Death dates were linked from the national population register. Only the last operated hip was considered for patients with bilateral THA.[@Bulow2020] Patients with missing information on, or an ASA class of IV and above, were excluded, as were patients with missing information on BMI or a measurement above 50. Patients with missing information on educational levels or the type of hospital performing index surgery were also excluded.

@@

Logistic LASSO regression was performed for each sample using the chosen $\lambda$ as penalty term. Regression coefficients were ranked based on their absolute values as a measure of variable importance. We then used Bayesian methods to estimate a posterior distribution and to identify two change points in a linear segmented piecewise regression model. The second change point was then used as a break-point. Influential predictors with absolute coefficients value above this point scored a point and the entire process was repeated 100 times, yielding 10,000 bootstrap samples in total. Potential predictors that were selected at least `r brlasso_selection_n["main"]` out of 100 times were then used in a main effects multivariable logistic regression model without penalty and without pre-normalization of numeric variables. An even more parsimonious "reduced" model with potential predictors chosen at least `r brlasso_selection_n["reduced"]` out of 100 times was evaluated for comparison. Univariable prediction models based on either ASA class, the Charlson, Elixhauser, or the Rx Risk V comorbidity indices were fitted for comparison, as well as multivariable models combining those measures with age, sex and BMI (10 models in total). The Rx Risk V index is a comorbidity index based on medical prescriptions coded by the Anatomical Therapeutic Chemical (ATC) classification system during one year prior to surgery. This data was retrieved from the Swedish national prescription register and classified according to Pratt et al.[@Pratt2018] Odds ratios for the final models were estimated with 95 % confidence intervals based on the whole cohort.

@@

**TODO:: Add XXX numbers for DK. Differences in Charlson/Elix might be discussed?**

@@

We found that a reduced prediction model based on some easily identifiable clinical conditions, sex, and BMI was better at predicting PJI within 90 days after THA than models based on either ASA class or the Charlson, Elixhauser or Rx Risk V comorbidity indices. This model performed better than the established comorbidity measures in terms of AUC, Nagelkerke's $R^2$ and calibration.

@@

Since the prediction model was based on easily accessible information it can be translated into a simple formula $\hat p = 1/[1 + \mathrm{exp}(-\hat \alpha - x'\hat \beta)]$ where $\hat p$ is the estimated probability, $\hat \alpha$ and $\hat \beta = (\hat\beta_1, \hat\beta_2, \ldots, \hat\beta_k)$ are the estimated intercept and coefficients (Tab. \@ref(tab:coefs)) and $x = (x_1, x_2, \ldots, x_k)$ are corresponding patient characteristics. For example, `r examples$desc[[1]]` would have a probability of $1/[1 + \mathrm{exp}(6.31 - 60\cdot0.02)] \approx$ `r examples$p[[1]]` of suffering from a PJI within 90 days, whereas `r examples$desc[[2]]` would have a probability of `r examples$p[[2]]`. Note, however, that observed proportions above 10 % were rare, and predicted probabilities above this limit are subject to extrapolation.

@@

Male sex is associated with an increased risk of developing PJI after arthroplasty surgery,[@Dale2012] and sex is included as a predictor variable in several previously developed risk calculators, which agrees with our findings.[@Wingert2016a; @Tan2018] Patients with liver cirrhosis are described to have a more than doubled risk of suffering from PJI within one year after THA, supporting our finding of the presence of liver diseases among our predictor variables.[@Deleuran2015] Taken together, the above cited findings support that the predictor variables in our models seem to be relevant in the context of predicting PJI.

@@

```{r aucci, fig.cap = "Area Under the Receiver Operation Characteristics Curve (AUC) as a measure of predictive discriminative ability with 95 % confidence intervals (De-Long). The reduced model performed no different than the main model on the Swedish data, and both of these models performed better than all other models (left panel). Similar models were fitted to the Danish cohort (right panel). Coefficient values based on the Swedish data, Reduced model (SE), performed almost as good as the reduced model (DK) with coefficient values refitted to the Danish cohort."}

@@

```{r sep, fig.cap = "Separation between patients with and without PJI within 90 days versus their predicted probabilities of this event. Most patients did not have PJI, wherefore the blue bars dominate the histogram (left panel; note the scales). A normalized density plot reveals, however, that patients with PJI had, on average, higher predicted probabilities for this adverse event (right panel)."}
knitr::include_graphics("../graphs/separation.png")
```

@@

```{r calibrationse, fig.cap = "This figure illustrates internal calibration of the reduced model, used in the Swedish cohort. Predicted probabilities are similar to observed proportions, as indicated by close proximity of the grey 95 % confidence band to the diagonal line, which indicates perfect calibration. Proportions of PJI above 10 % were rarely observed and therefore omitted."}
knitr::include_graphics("../graphs/calibration.png")
```

@@

tibble(
  classification = c("ICD-10", "NOMESCO"),
  codes = c(icd10_codes, nomesco_codes)
) %>% 
  knitr::kable(
    caption = "Codes identifying PJI if recorded in the national patient register within 90 days after THA."
  )

@@

```{r fni}
tab_new_info %>% 
  arrange(desc(`R2 (%)`)) %>% 
knitr::kable(
  caption = "Model performance based on the Swedish derivation cohort. The area under the receiver operating characteristics curve (AUC) is a measure of discriminatory ability. Nagelkerke's pseudo-coefficient of determination (R2) is an estimate of the proportion of explained variance for each model (the correlation between observed and predicted values). The univariable Charlson model had the lowest R2 and was therefore used as reference for the fraction of new information (FNI) added by the other models.")
```

@@

```{r coefs}
tbl_coefs_present %>% 
  mutate(
    beta = round(beta, 2)
  ) %>% 
knitr::kable(
  caption = 'Estimated coefficients (beta) and odds ratios (OR) with 95 % confidence intervals for the reduced models. BMI = body mass index (under/normal weight as baseline). CNS = central nervous system.'
)
```

@@

Variable selection and coefficient estimates were based on the Swedish cohort. 
The reduced model was then used to predict PJI also in Denmark. The coefficient values of the reduced model were also re-fitted to the Danish cohort for comparison. We compared the estimates from the Swedish and Danish cohort and found most values to be of similar magnitude. The only coefficient with reversed direction was for patients with a diagnose of "sequelae after childhood hip disease". This is a rare condition, with very few observed PJI:s within 90 days. We also re-estimated the model coefficients 1,000 times based on the Swedish data. Each time, we took a random sample of the same size ($N = 18,854$) as was observed in the Danish cohort. The 2.5th and 97.5th percentiles were then used to form empirical 95 % confidence intervals for each coefficient (Tab. \@ref(tab:comparecoefs) and Fig. \@ref(fig:coefsspread)). The estimated effect of "sequelae after childhood hip disease" fall outside this empirical CI. Applying multiplicity correction by Bonferroni or similar, would eliminate this significance. Hence, it seems that both cohorts are similar in respect to association between the studied covariates and the risk of PJI within 90 days of THA.

```{r comparecoefs}
compare_se_dk_coefs %>% 
  rename(`95 % CI` = CI) %>% 
knitr::kable(
  caption = "Estimated coefficients for the reduced model based on the Swedish derivation cohort (Swedish), as well as re-estimated coefficient values based on the Danish cohort (Danish). Empirical confidence intervals (95 % CI) based on 1,000 resamples from the Swedish cohort of the same sample size (N = 18,854) as used in the Danish cohort."
)
```

```{r coefsspread, fig.cap = "Estimated coefficient values for the reduced model. Red triangles indicate estimates from the Swedish derivation data set. Red circles indicate re-estimated coefficient values for the same model based on the Danish validation cohort. Small coulored dots are empirical estimates from 1000 subsamples based on the Swedish data set, of the same sample size as used in the Danish validation cohort. Black dots indicate the outer limits of 95 % empirical confidence intervals. The Danish estimates almost always fall within those CIs."}
knitr::include_graphics("../validation/Swedish_model.png")
```
